Poincar\'e--Friedrichs constants over triangulated domains

### 2024-04-30 main.tex
spellcheck

\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\input{header}
\usepackage{amscd}
\usepackage{tikz-cd}
\newtheorem{remark}{Remark}

@@

While it is known that finite element patches admit Poincar\'e--Friedrichs inequalities, 
we are not aware of computable estimates. 
Clearly, not all local patches describe convex subdomains. 
An ostensibly more practical class of domains are domains star-shaped with respect to a ball.
Indeed, finite element patches of Lipschitz satisfy that condition. 
Over patches around interior subsimplices, the size of interior ball only depends on the shape regularity of the triangulation. However, the interior ball can be abstrarily small when the patch is around a boundary simplex at a reentrant corner, even if the mesh has good shape-regularity. 
Some interesting limit cases include the slit domain and the crossed bricks domain,
for which some finite element patches are not star-shaped with respect to any ball. 
\color{red}Our upper bounds do not depend on the angles of such reentrant corners, even in the aforementioned limit cases, but only the shape-regularity of the triangulation. \color{black}

>>>>

\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\input{header}

@@

While it is known that finite element patches admit Poincar\'e--Friedrichs inequalities, 
we are not aware of computable estimates. 
Clearly, not all local patches describe convex subdomains. 
An ostensibly more practical class of domains are domains star-shaped with respect to a ball.
Indeed, finite element patches of Lipschitz satisfy that condition. 
Over patches around interior subsimplices, the size of interior ball only depends on the shape regularity of the triangulation. However, the interior ball can be arbitrarily small when the patch is around a boundary simplex at a reentrant corner, even if the mesh has good shape-regularity. 
Some interesting limit cases include the slit domain and the crossed bricks domain,
for which some finite element patches are not star-shaped with respect to any ball. 
\color{red}Our upper bounds do not depend on the angles of such reentrant corners, even in the aforementioned limit cases, but only the shape-regularity of the triangulation. \color{black}
